---
title: "Supplementary Materials"
format:
  pdf:
    fig-height: 12
    fig-width: 12
knitr:
  opts_knit:
    root.dir: "C:/Users/I_RICHMO/Documents/Repositories/RuellesVertes"
---

***Testing a rapid assessment approach for measuring ecosystem services in urban green alleys***

S2. Model diagnostic plots

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| include: false
#| label: setup


library(targets)
tar_source('R')

tar_load(model_max_temp)
tar_load(model_min_temp)
tar_load(model_noise)
tar_load(model_habitat)
tar_load(model_food)
```

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: max-temp-ruelle

print(resid_plots(model_max_temp[[1]]$veg_Avg_max_daily_temp, ""))

```

Figure 1. Diagnostic plots for average maximum temperature, as a function of ruelle length, ruelle area, average groundcover, average midstorey cover, and average canopy cover.

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: max-temp-buffer

print(resid_plots(model_max_temp[[2]]$Avg_max_daily_temp_50, ""))

```

Figure 2. Diagnostic plots for average maximum temperature, as a function of percent vegetation, percent building, percent canopy, and road area within a 50 m buffer.

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: min-temp-ruelle

print(resid_plots(model_min_temp[[1]]$veg_Avg_min_daily_temp, ""))

```

Figure 3. Diagnostic plots for average minimum temperature, as a function of ruelle length, ruelle area, average groundcover, average midstorey cover, and average canopy cover.

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: min-temp-buffer

print(resid_plots(model_min_temp[[2]]$Avg_min_daily_temp_50, ""))

```

Figure 4. Diagnostic plots for average minimum temperature, as a function of percent vegetation, percent building, percent canopy, and road area within a 50 m buffer.

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: noise-ruelle

print(resid_plots(model_noise[[1]]$veg_mean_NDSI, ""))

```

Figure 5. Diagnostic plots for average normalized difference sound index (NDSI), as a function of ruelle length, ruelle area, average groundcover, average midstorey cover, and average canopy cover.

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: noise-buffer

print(resid_plots(model_noise[[2]]$mean_NDSI_50, ""))

```

Figure 6. Diagnostic plots for average normalized difference sound index (NDSI), as a function of percent vegetation, percent building, percent canopy, and road area within a 50 m buffer.

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: floral-ruelle

print(resid_plots(model_habitat[[1]]$veg_Floral_coverage_per_m2, ""))

```

Figure 7. Diagnostic plots for floral coverage (per m2), as a function of ruelle length, ruelle area, average groundcover, average midstorey cover, and average canopy cover.

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: food-ruelle

print(resid_plots(model_food[[1]]$veg_Food_coverage_per_m2, ""))

```

Figure 8. Diagnostic plots for food coverage (per m2), as a function of ruelle length, ruelle area, average groundcover, average midstorey cover, and average canopy cover.
