---
title: "Model Summary & Update"
format: html
knitr:
  opts_knit:
    root.dir: "C:/Users/I_RICHMO/Documents/Repositories/ruelles-vertes"
---

```{r, echo = F, eval = T, message = F, warning = F}
source('R/packages.R')

```

# New Model Structure

## Hypothesis-Based

Most of the changes to the model approach is based on the desire to make our work more rooted in hypotheses, which I think makes it more easier to interpret. In addition, due to our low sample size (n = 24), splitting models into groups of explanatory variables reduces the risk of overfitting.

### Explanatory Variables

+-------------------------+---------------------------+--------------------+
| Group                   | Variable                  | Unit               |
+=========================+===========================+====================+
| Vegetation Within Alley | Canopy cover              | \%                 |
+-------------------------+---------------------------+--------------------+
|                         | Midstorey cover           | \%                 |
+-------------------------+---------------------------+--------------------+
|                         | Ground cover              | \%                 |
+-------------------------+---------------------------+--------------------+
| Alley Structure         | Alley length              | metres             |
+-------------------------+---------------------------+--------------------+
|                         | Alley area                | metres^2^          |
+-------------------------+---------------------------+--------------------+
| Aesthetic Features 1    | Public art                | common/rare/absent |
+-------------------------+---------------------------+--------------------+
|                         | Children's play equipment | common/rare/absent |
+-------------------------+---------------------------+--------------------+
|                         | Maintained structures     | common/rare/absent |
+-------------------------+---------------------------+--------------------+
| Aesthetic Features 2    | Wildlife support          | common/rare/absent |
+-------------------------+---------------------------+--------------------+
|                         | Maintained gardens        | common/rare/absent |
+-------------------------+---------------------------+--------------------+
| Surrounding Land Cover  | Canopy cover              | \%                 |
|                         |                           |                    |
| (50 m & 100 m)          |                           |                    |
+-------------------------+---------------------------+--------------------+
|                         | Vegetation cover          | \%                 |
+-------------------------+---------------------------+--------------------+
|                         | Building cover            | \%                 |
+-------------------------+---------------------------+--------------------+
|                         | Impervious cover          | \%                 |
+-------------------------+---------------------------+--------------------+
|                         | Road area                 | metres^2^          |
+-------------------------+---------------------------+--------------------+

### Models

Temperature:

$$
Temp \sim Vegetation \ within \ alleys \ + \ Alley \ structure
$$ $$
Temp \sim Surrounding \ land \ cover \ 50m
$$ $$
Temp \sim Surrounding \ land \ cover \ 100m
$$

Noise:

$$
Noise \sim Vegetation \ within \ alleys \ + \ Alley \ structure
$$

$$
Noise \sim Aesthetic \ features  \ 1
$$

$$
Noise \sim Aesthetics \ features \ 2
$$\

$$
Noise \sim Surrounding \ land \ cover \ 50m
$$ $$
Noise \sim Surrounding \ land \ cover \ 100m
$$

Habitat Provisioning:

$$ Habitat \sim Vegetation \ within \ alleys \ + \ Alley \ structure $$

$$ Habitat \sim Aesthetic \ features  \ 2 $$

Food Provisioning:

$$ Food \sim Vegetation \ within \ alleys \ + \ Alley \ structure $$

$$ Food \sim Aesthetic \ features  \ 1 $$

$$ Food \sim Aesthetics \ features \ 2 $$

# Model Outputs

```{r, echo = F, eval = T}
tar_load(model_max_temp)


```
